Thickness optimization in wide range quasi omnidirectional 1-D photonic structures

### 2020-12-31 PaperVictor.tex
Revise introduction

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano} averaged over a wide wavelength
and angular range  of PS-based mirrors with different
porosity contrasts searching for a minimum thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and \textit{stacking} sub-mirrors. The
chirped structures were better suited for the Vis, and the stacked
sub-mirrors for the NIR regions. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PhC)-based structures are extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be limited by photonic band gaps (PBGs)
where transmission states are forbidden. The PhC  shows a
PBG corresponding to the electromagnetic modes which are not allowed to propagate
through the structure and behaves as a perfect mirror for that range. The width of
reflection spectrum is important while designing an omnidirectional mirror for
different applications. The metallic mirrors are widely accepted for reflection
purposes, but widespread use is limited due to their absorptive nature at the
visible and near infrared frequencies.  A good alternative are dielectric
structures as they also provide design flexibility in terms of
reflection wavelength. These properties are widely used to design various
one-dimensional (1D) and two-dimensional (2D) PhCs for its
potential applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1DPhC is composed of alternating high $\left(
n_{H}\right) $ and low $\left(n_{L}\right) $ refractive index layers (Bragg Mirror,
BM). The optical thicknesses are typically chosen to be quarter-wavelength length, $
n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$, at some operating wavelength $\lambda_{0}$ 
(center wavelength) to obtain a certain
omnidirectional band gap. As the gap depends on the contrast of the
refractive indices and the number of periods,  broadband mirrors can  be
engineered by modulating the reflection in a broader wavelength range.
One of the ways to obtain such structures has been the continuous variation of
thicknesses along the depth, defined as \textit{chirped}-type \cite{Zipock1997}
structures. Additionally, broader mirrors can also be achieved by overlapping
different BMs, where each one reflects around a specific central wavelength,
resulting in a wider photonic band gap \cite{Xifre2009}.

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al., \cite{Chen1999} have
reported an ODBM of about 70 nm in NIR range designed with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ deposited using sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs$/$AlAs layers,
followed by its conversion to a multilayer stack of GaAs/Al$_{2}$O$_{3}$ by selective
oxidation of the AlAs layers, to obtain an ODBM with a gap from 710 to 950
nm. On the other hand, DeCorby et al., \cite{DeCorby2005} fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain 150 nm wide omnidirectional band, centered at 1750 nm
wavelength. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate 1DPhC of TiO$_{2}$/SiO$_{2}$ and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and
require sophisticated equipment and long fabrication time. Using PS
is an alternative, as PS is typically fabricated by simple electrochemical etching of
crystalline Si in hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air in a relatively short duration of
time. The generated porosity can be tuned by changing the applied current
density and hence modifies the refractive index of the resulting PS. This
fact opens the possibility of designing 1DPhC with PS, which seeks to
control the propagation of light in a dielectric medium. The low cost and
ease of obtaining porous silicon make it an excellent candidate to develop
optical devices based on multilayer structures \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common 
application of porous silicon, they have been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}. In particular, PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR) \cite{Bruyant2003}. Keeping
in view that high values of average porosity, refractive index contrast and
thickness make the multilayer structures fragile, in this work various wide
band gap photonic structures have been proposed to obtain maximal average
reflectance (R$_{\text{ave}}\left( \lambda ,\theta \right) $) with the minimum
possible thickness and low refractive index contrast.

This paper is organized as follows. Section 2 presents the development of
methods used to design and calculate the reflectance spectra of the PS
multilayer structures. Section 3 provides the experimental details about the
fabrication of some of these structures. Section 4 presents the numerical
results corresponding to different methodologies (chirped structures and sub-mirror stacks) adopted to minimize the thickness of the structure for
maximal reflectance along with the experimental results and its comparison with the
existing reports.  The obtained experimental results revealed an enhancement in the
quasi omnidirectional band gap (0-60${{}^\circ}$) by a factor of approximately 2
with half the structure physical thickness in both the configurations, compared to
the last reported works \cite{DelRio2018,Chavez2020}. Finally, the conclusions of
this work are presented in Section 5.

\section{Theoretical analysis}

In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the
reference). Under the consideration that the system only varies along the $z$ axis, the 
transfer matrix is $M\left(z_{2},z_{1}\right)$
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$ 
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters.
The development of $M$ is shown in the supplementary information. Therefore, the
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous
layers in the simulations were obtained by Bruggeman effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

\section{Experimental details}

@@

\section{Results and discussion}

@@

\section{Conclusion}

>>>>

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the reflectance ($\braket{R_{\text{ave}}}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors  averaged over a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We found \notaL{No
  estoy seguro del tiempo} that
chirped structures were better suited for the Vis stacked
sub-mirrors for the NIR region. We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
withinin a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses of is quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at some chosen nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type \cite{Zipock1997}
structures. An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band
\cite{Xifre2009}.
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} have
reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al., \cite{Park2003}
used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective
oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al., \cite{Jena2019}
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has
increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce photonic mirrors
that have a large reflectance over a wide band-width with a relatively
small thickness and refractive index contrast. Specifically, our aim
is to maximize the reflectance $R$ averaged over a wide range of
wavelengths $\lambda$ and angles of incidence $\theta$.

This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
  usa referencias a etiquetas para numerar y referir todo} we develop the
methods used to design and calculate the reflectance spectra of the PS
multilayered structures such as chirped structures and mirror
stacks. In Sec. \ref{s:exp} we provide details about the
fabrication of these structures. In Sec. \ref{s:res} we present the numerical
and experimental results for our proposed structures and compare
them to previous reports. We obtained significantly larger band-widths
with significantly thinner structures. \notaL{Dejo para resultados y
  conclusiones los detalles de con quién comparamos y qué salió.}
Finally, we discuss our conclusions in Section \ref{s:conc}.

\section{Theoretical analysis}\label{s:theory}

\notaL{Pon etiquetas a todo para poderlo referir}
In the analysis of the propagation of the electromagnetic field through
multilayer systems, it is common to employ the transfer matrix method (put the
reference). Under the consideration that the system only varies along the $z$ axis, the
transfer matrix is $M\left(z_{2},z_{1}\right)$
a 2x2 matrix that relates the components of the electric field E$_{\parallel }$
and the magnetic field H$_{\parallel }$ parallel to the $xy$ plane, and
normal to the axis of the structure, evaluated at any two points $z_{2}$
and $z_{1}$
\begin{equation*}
\left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\Vert } \\
H_{\Vert }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
to calculate the reflectance of large multilayer systems proposed by Puente-D%
\'{\i}az, et al. \cite{Puente2020}, since we need a reliable and stable tool
to design an optimized structure through a minimization procedure that
requires the calculation of complete spectra for all sets of design parameters.
The development of $M$ is shown in the supplementary information. Therefore, the
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}\tilde{M}_{11}+\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}_{21}-Z_{s}%
\tilde{M}_{22}}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha }}{Z_{0}\tilde{M}_{11}-\tilde{M}_{12}-Z_{0}Z_{s}\tilde{M}%
_{21}+Z_{s}\tilde{M}_{22}},  \label{tBloch}
\end{equation}%
where the upper sign $-$ in Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively. Furthermore, $\tilde{M}_{ij}$ are the elements of the transfer matrix. As usual, the reflectance is given by $R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=Z_{0}/Z_{s}$ for the case of TE polarization and $\beta =Z_{s}/Z_{0}$ for
the case of TM polarization. Additionally, complex refractive indices of the porous
layers in the simulations were obtained by Bruggeman effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

\section{Experimental details}\label{s:exp}

@@

\section{Results and discussion}\label{s:res}

@@

\section{Conclusion}\label{s:conc}
